Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-15 writeup/gz_hubble_data.tex
Forcing in @Mel23's changes to threshold table

The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically-pure sample. In Table~\ref{tab:prev_tasks} we offer baseline cuts for selecting galaxies of a variety of morphologies. {\note As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$} These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled. In this example, such galaxies are featured, non-clumpy, non-edge~on galaxies, or featured, clumpy, spiral galaxies. At this point a cut can be made on $p_{\rm bar}$ to select a clean sample of only strong bars $p_{\rm bar}>0.8$, or a complete sample of weak and strong bars $p_{\rm bar}>0.3$, or the value most appropriate to the science case.

@@

\begin{table*}
\caption{Cookbook \label{tab:prev_tasks}}
\begin{tabular}{llll}
\hline\hline
Task No. &  Task 	        & Previous Task  & Vote Fraction Cut \\
         &            	        &                & $N_{task} \ge 20$ \\
\hline
01       & smooth or features   &  -                  & -                 \\
02       & edge on              & 01, 12              & $p_{\rm clumpy,no}>0.55$              \\
03       & bar		            & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
04       & spiral arms          & 01, 12, 02          & $p_{\rm edgeon,no}>$                  \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
05       & bulge prominence     & 01, 12, 02          & $p_{\rm edgeon,no}>$                 \\
         &                      & 01, 12, 16, 15      & $p_{\rm arrangement,spiral}>$         \\
06       & odd yes/no           & -                   &                   \\
07       & rounded              & 01                  & $p_{\rm smooth}>0.45$               \\
08       & odd feature          & 06                  & $p_{\rm odd,yes}>$                  \\
09       & bulge shape          & 01, 12, 02          & $p_{\rm edgeon,yes}>$               \\
10       & arms winding         & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                  \\
         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
11       & arms number          & 01, 12, 02, 04      & $p_{\rm spiral,yes}>$                 \\
         &                      & 01, 12, 16, 15, 04  & $p_{\rm spiral,yes}>$                  \\
12       & clumpy               & 01                  & $p_{\rm features}>0.52$              \\
13       & bright clump         & 01, 12, 16          & $p_{\rm one clump}<$                 \\
14       & bright central clump & 01, 12, 16, 13      & $p_{\rm bright clump,yes}>$           \\
15       & clump arrangement    & 01, 12, 16          & $p_{\rm one clump}<$                \\
16       & clump count          & 01, 12              & $p_{\rm clumpy,yes}>0.55$              \\
17       & clumps symmetrical   & 01, 12, 16          & $p_{\rm one clump}<$                \\
18       & clumps embedded      & 01, 12, 16          &  $p_{\rm one clump}<$                 \\

\hline\hline
\end{tabular}
\end{table*}

>>>>

The flexibility of this catalog allows the user to set their own selection criteria for vote fraction thresholds to create a morphologically-pure sample. In Table~\ref{tbl:thresholds} we offer baseline cuts for selecting galaxies of a variety of morphologies. {\note As an example: to select barred galaxies, one should select objects with $p_{\rm features}>0.52, p_{\rm clumpy,no} > 0.55,$ and $p_{edgeon,no}>x.xx$ \emph{or} objects with $p_{\rm features}>0.52, p_{\rm clumpy,yes} > x.xx, (p_{\rm clump~count, 3}+p_{\rm clump~count,4}+p_{\rm clump~count,>4}+p_{\rm clump~count,can't~tell})>x.xx,$ and $p_{\rm clump~arrangement,spiral}>x.xx.$} These cuts define a sample of galaxies of ``bar candidates''; ie galaxies for which answering the bar question makes physical sense and the vote fraction $p_{\rm bar}$ is well-sampled. In this example, such galaxies are featured, non-clumpy, non-edge~on galaxies, or featured, clumpy, spiral galaxies. At this point a cut can be made on $p_{\rm bar}$ to select a clean sample of only strong bars $p_{\rm bar}>0.8$, or a complete sample of weak and strong bars $p_{\rm bar}>0.3$, or the value most appropriate to the science case.

@@

\begin{table}
\caption{Suggested thresholds for selecting morphological samples from Galaxy Zoo: Hubble \label{tbl:thresholds}}
\begin{tabular}{llll}
\hline\hline
No.      &  Task 	            & Previous              & Vote fraction threshold            \\
         &            	        & task(s)               & $N_{\rm task} \ge 20$              \\
\hline
01       & smooth or features   & $-$                   & $-$                                \\
02       & edge on              & 01, 12                & $p_{\rm clumpy,no}>0.30$            \\
03       & bar		            & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
04       & spiral arms          & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
05       & bulge prominence     & 01, 12, 02            & $p_{\rm edgeon,no}>0.25$           \\
         &                      & 01, 12, 16, 15        & $p_{\rm clumpy~spiral}>0.65$  \\
06       & odd yes/no           & $-$                   & $-$                                \\
07       & rounded              & 01                    & $p_{\rm smooth}>0.70$               \\
08       & odd feature          & 06                    & $p_{\rm odd,yes}> 0.50$            \\
09       & bulge shape          & 01, 12, 02            & $p_{\rm edgeon,yes}>0.40$           \\
10       & arms winding         & 01, 12, 02, 04        & $p_{\rm spiral,yes}>0.25$          \\
11       & arms number          & 01, 12, 02, 04        & $p_{\rm spiral,yes}>0.25$          \\
12       & clumpy               & 01                    & $p_{\rm features}>0.23$            \\
13       & bright clump         & 01, 12, 16            & $p_{\rm one~clump}< 0.40$           \\
14       & bright central clump & 01, 12, 16, 13        & $p_{\rm bright~clump,yes}>0.50$     \\
15       & clump arrangement    & 01, 12, 16            & $p_{\rm multiple~clumps}>0.45$     \\
16       & clump count          & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
17       & clumps symmetrical   & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
18       & clumps embedded      & 01, 12                & $p_{\rm clumpy,yes}>0.80$           \\
\hline\hline
\end{tabular}
\end{table}
